Toward theories of deliberated preferences

### 2020-08-14 simple.tex
Started new pref descr

\section{Preferences}
\subsection{Preferences}
Let $\allalts$ be a set of alternatives. Define $\Phi_\allalts = \{\phi_{a \pst b} \suchthat a ≠ b \in \allalts\} \cup \{\phi_{a \peq b} \suchthat a ≠ b \in \allalts\}$, with $\phi_{a \pst b}$ intuitively representing a strict preference of $i$ for $a$ against $b$, and $\phi_{a \peq b}$ intuitively representing a weak preference of $i$ for $a$ against $b$. Define $¬\phi_{a \pst b} = \phi_{b \peq a}$ and $¬\phi_{a \peq b} = \phi_{b \pst a}$.

>>>>

\section{Preferences}
\subsection{Preferences, better}
Let $\allalts$ be a set of alternatives.

A choice prediction $C_\gamma: \powersetz{\allalts} → \powersetz{\powersetz{\allalts}}$ is a mapping from each possible bundle $\emptyset ≠ B \subseteq \allalts$ to a non-empty set $\emptyset ≠ C_\gamma(B) = \mathcal{C} \subseteq \powersetz{B}$ of non-empty sets of alternatives included in the bundle. 
Thus, a generic element $\alts \in C_\gamma(B)$ satisfies $\emptyset ≠ \alts \subseteq B$. 
The choice prediction given a bundle $B$ predicts that $i$ will, given $B$, choose some indifference set that includes one of the elements $\alts \in C_\gamma(B)$.

Define $\Phi_\allalts = \set{\phi_{B, a \ind b} \suchthat \emptyset ≠ B \subseteq \allalts, a ≠ b \in B} \cup \set{\phi_{B, ¬a} \suchthat \emptyset ≠ B \subseteq \allalts, a \in B}$.

Given $\emptyset ≠ B \subseteq \allalts$, define $\emptyset ≠ B_{\hist, i} \subseteq B$ as the subset that $i$ chooses as her indifference choice after exposure to $\hist$.
Define $\hist \ileadsto \phi_{B, a \ind b}$ iff $[a \in B_{\hist, i} ⇔ b \in B_{\hist, i}]$.
Define $\hist \ileadsto \phi_{B, ¬a}$ iff $a \notin B_{\hist, i}$.

Given $a ≠ b$, define $a \peq b$ iff $\forall \set{a, b} \subseteq B: \phi_{B, a \ind b} \in \gPhi \lor \phi_{B, ¬b} \in \gPhi$.

In order to be as resolute as possible, define an arbitrary connected ordering $>$ on $\allalts$ (a transitive, asymmetric and connected relation, connected meaning that $\forall a ≠ b \in \allalts:  [a > b \lor b > a]$), used to break indifference. Define $a \pst b$ iff $[a \peq b \land (b \npeq a \lor a > b)]$.

Old approach follows.

Define $\Phi_\allalts = \set{\phi_{B, \mathcal{C}} \suchthat \emptyset ≠ B \subseteq \allalts, \mathcal{C} \subseteq \powersetz{B}}$.

$\gamma$ gives, for each 
Define $\phi_{(B_k), B}$: $\hist \ileadsto \phi$ iff given $B$, $i$ chooses some $B_{\hist, i} \subseteq B$ such that $\exists B_k \subseteq B_{\hist, i}$.

Define $a \peq b$ iff $\forall \set{a, b} \subseteq B: [\exists \set{a, b} \subseteq B_k \lor (\exists a \in B_k \land \nexists b \in B_k)]$.

Define $a \pst b$ iff $a \peq b \land b \npst a$.

To prove. 1) $\peq$ is transitive. 2) If $a \pst b$, then $b$ is never chosen by $i$ when $a$ is present: $\forall \phi_{B_k} \in \iPhi: $ no $B_k$ contain $b$.

\subsection{Preferences}
Let $\allalts$ be a set of alternatives. Define $\Phi_\allalts = \{\phi_{a \pst b} \suchthat a ≠ b \in \allalts\} \cup \{\phi_{a \peq b} \suchthat a ≠ b \in \allalts\}$, with $\phi_{a \pst b}$ intuitively representing a strict preference of $i$ for $a$ against $b$, and $\phi_{a \peq b}$ intuitively representing a weak preference of $i$ for $a$ against $b$. Define $¬\phi_{a \pst b} = \phi_{b \peq a}$ and $¬\phi_{a \peq b} = \phi_{b \pst a}$.
